A Technique for Inter-Retailer Recommendations

### 2014-06-12 paper2/paper.tex
Made plot labels bigger

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible. This plot was generated on the
    Women's Dresses category.}
    \label{fig:PopularityHistogram}
\end{figure}

@@

\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline

\end{tabular}
\end{center}

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}

\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

@@

\section*{Appendix}

>>>>

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=1.0\textwidth]{PopularityHistogram2.png}
	\caption{The top 25 most popular items and how many times they appear in
    recommendations. Here we compare the distribution of gold-standard
    recommendations (red) to the recommendations predicted by the
    $LatentFeatureRecommender$ with (blue) and without (yellow) popularity. The
    yellow bars are small and barely visible. This plot was generated on the
    Women's Dresses category.}
    \label{fig:PopularityHistogram}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{ | l || c | c | c || c | c | c |}
\hline
Recommender & Precision & Recall & F1 Score & 2-Precision & 2-Recall & 2-F1 Score \\ \hline\hline
$Random$ & .002 & .001 & .001 & .021 & .008 & .012 \\ \hline
$Popularity$ & .016 & .019 & .017 & .080 & .096 & .087 \\ \hline
$RandomMap$ & .014 & .019 & .016 & .070 & .095 & .081 \\ \hline
$OneModel$ & .103 & .132 & .116 & .404 & .410 & .407 \\ \hline
$ContentBased$ & .014 & .020 & .016 &
\textbf{.115} & \textbf{.186} & \textbf{.142} \\ \hline 
$Neighborhood$ & .040 & .060 & .048 &
\textbf{.137} & \textbf{.240} & \textbf{.175} \\ \hline 
$LatentFeature$ & .036 & .060 & .045 &
\textbf{.174} & \textbf{.228} & \textbf{.197} \\ \hline
\end{tabular}
\caption{The performance of each of the recommenders across all categories. The
first five are the baseline recommenders outlined in the previous section. The
final three are the recommenders of interest, described in the Recommender
Algorithms section. The scores in bold are the most important results and are 
further illustrated in the following figure.}
\end{center}
\end{table}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.65\textwidth]{RecommenderPerformance2.png}
	\caption{The performance of the three main recommenders in terms of
    2-metrics across all categories. We emphasize the 2-F1 Score as our most
    important single metric of comparison. We see that the $LatentFeatureRecommender$
    outperforms the other recommenders in this score.} 
    \label{fig:RecommenderPerformance} 
\end{figure}
\pagebreak
\section*{Conclusion}
In this study, we address the problem of determining inter-retailer, or
inter-catalogue, item-item associations. We frame this problem as a recommender
problem, which motivates a relatively straightforward experiment in which a
candidate algorithm must connect two recommendation graphs by guessing edges
between them.

@@
